Cryptographic assurance of secrecy and fairness in voting

### 2012-12-08 paper/paper.tex
pret-a

Once votes have been collected, it is the responsibility of the election authority to tally votes for the various
candidates in a race and publish \emph{accurate} tallies. Generally, the electorate is reliant on
\emph{someone} to provide these tallies. But it is much less common for voters themselves to have
the opportunity to verify that the votes were tallied \emph{exactly} as they were cast.

@@

\term{\pv{}} accomplishes this process via a \term{mixnet}: a set of mix servers each secretly shuffle and transform, in turn, the set of encrypted votes in a verifiable way.
\term{\pv{}} is flexible enough to use either a decryption or re-encryption mixnet, and with the latter, a variety of encryption schemes.
Scratch \& Vote \cite{scratch}, a variation on \term{\pv}, tallies the votes homomorphically rather than with a mixnet.

@@

Auditors are then provided with proofs for verification of proper mixing (see later analysis). Once
auditors are satisfied, \term{Helios} decrypts and tallies the ballots. Similarly, \term{Helios}
proves that ballot decryptions are accurate using a challenge-response zero-knowledge scheme
known as the \term{Chaum-Pedersen protocol}, through which the system proves that \emph{all}
decrypted ballots are in fact correct plaintexts for the corresponding mixnet outputs. Challenges
are generated by the system using a technique similar to that employed to provide mixnet proofs.

@@

In both \term{Scantegrity} and \term{Helios}, the following information is revealed after the election:
\begin{itemize}
	\item
		\emph{Some} information about \emph{all} encrypted ballots, linked to voters.
	\item
		\emph{All} decrypted ballots, \emph{not} linked to voters.
\end{itemize}

@@

Where Table R lies between encryptions and decryptions in \term{Scantegrity}, \term{\pv{}} and \term{Helios} makes use of a
cryptographic \term{mixnet} -- performed with cast ballots in hand -- to prevent an attacker from
tracing a vote to its decryption. Unlike in \term{Scantegrity}, \emph{all} encrypted votes can be traced to
their mixnet input, and \emph{all} mixnet outputs can be traced to a location in the tally; however,
those one cannot connect those two traces, such that secrecy is preserved.

@@

\term{Helios} must prove to auditors that ballots have been properly mixed. To do so, \term{Helios}
shuffles the votes multiple times, actually using only the final shuffle in tallying the results.
The other shuffles, referred to as ``shadow mixes'', are made public. Those mixes are hashed to
obtain a bit string that is used, bit-for-bit, as a set of challenges, with one bit value indicating
that \term{Helios} must provide the permutation used for the shuffle and the $s_{i}$ values used for
re-encryption, and the other bit value indicating that it must provide a mapping from one shadow mix
to another. This is known as a challenge-response \term{Honest-Verifier Zero-Knowledge} proof, and the
use of a hash to obtain the set of challenges allows this process to be completed entirely within
the \term{Helios} system -- without human involvement -- for publication and auditor verification.

In some ways, \term{Helios} count verification is simpler than that in \term{Scantegrity}. We have already
discussed how \term{Helios} uses a mixnet to achieve ballot secrecy. Once votes have been mixed using this
mechanism, they are decrypted, and so the actual plaintext ballots are exposed. From that point,
tallying is straightforward and trivially-verifiable via simple arithmetic.

\term{\pv{}} provides for verification of counting using techniques seen in both \term{Scantegrity}
and \term{Helios}: a mixnet proof based on randomized partial checking in which a random selection
determines points in the mixnet for which a mix server must show how it has mixed a particular vote.
Though it is not permitted for this selection to trace any one vote throughout the mixnet in order
to preserve privacy, it provides sufficient proof that the overall mixnet has shuffled votes
accurately.

As with \term{Helios}, votes are decrypted after exiting the mixnet and can tallied in a
trivially-verifiable manner.

@@

>>>>

Once votes have been collected, it is the responsibility of the state to tally votes for the various
candidates in a race and publish \emph{accurate} tallies. Generally, the electorate is reliant on
\emph{someone} to provide these tallies. But it is much less common for voters themselves to have
the opportunity to verify that the votes were tallied \emph{exactly} as they were cast.

@@

\term{\pv{}} accomplishes this process via a \term{mixnet}: a set of mix servers each secretly shuffle and transform, in turn, the set of encrypted votes in a verifiable way.
\term{\pv{}} is flexible enough to use either a decryption or reencryption mixnet, and with the latter, a variety of encryption schemes.
Scratch \& Vote \cite{scratch}, a variation on \term{\pv}, tallies the votes homomorphically rather than with a mixnet.

@@

In order to provide a guarantee of proper shuffling, \term{Helios} shuffles the votes multiple
times, actually using only the final shuffle in tallying the results. The other shuffles,
referred to as ``shadow mixes'', are made public. Those mixes are hashed to obtain a bit string
that is used, bit-for-bit, as a set of challenges, with one bit value indicating that \term{Helios} must
provide the permutation used for the shuffle and the $s_{i}$ values used for re-encryption, and the
other bit value indicating that it must provide a mapping from one shadow mix to another. This is
known as a challenge-response ``Honest-Verifier Zero-Knowledge'' proof, and the use of a hash to
obtain the set of challenges allows this process to be completed entirely within the \term{Helios} system
-- without human involvement -- for publication and auditor verification.

Once auditors are satisfied with the proofs, \term{Helios} decrypts and tallies the ballots. Similarly,
\term{Helios} proves that ballot decryptions are accurate using a challenge-response zero-knowledge scheme
known as the \term{Chaum-Pedersen protocol}, through which the system proves that \emph{all}
decrypted ballots are in fact correct plaintexts for the corresponding mixnet outputs. Challenges
are generated by the system using a technique similar to that employed to provide mixnet proofs.

@@

In all three systems, the following information is revealed after the election:
\begin{itemize}
	\item
		\emph{Some} information about \emph{all} encrypted ballots, linked to voters.
	\item
		\emph{All} decrypted ballots, \emph{not} linked to voters.
\end{itemize}

@@

Where Table R lies between encryptions and decryptions in \term{Scantegrity}, \term{\pv{}} and \term{Helios} make use of a
cryptographic \term{mixnet} -- performed with cast ballots in hand -- to prevent an attacker from
tracing a vote to its decryption. Unlike in \term{Scantegrity}, \emph{all} encrypted votes can be traced to
their mixnet input, and \emph{all} mixnet outputs can be traced to a location in the tally; however,
those one cannot connect those two traces, such that secrecy is preserved.

@@

In some ways, \term{Helios} count verification is simpler than that in \term{Scantegrity}. We have already
discussed how \term{Helios} uses a mixnet to achieve ballot secrecy. Once votes have been mixed using this
mechanism, they are decrypted, and so the actual plaintext ballots are exposed. From that point,
tallying is straightforward.

@@

In \term{\pv{}}, the secrets are the layered permutations of the candidate list corresponding to each ballot as encoded in its onion.
During the tallying phase, the end-to-end mapping from encrypted to decrypted ballot must also be concealed from any single party.
